A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Add figure

%%We further investigate the type of input passed to \eval in
%%Figure~\cite{fig:eval-expr-type} by the type of input and
%%the source of \eval. In this figure, \emph{Expression} is the type of program text,
%%\emph{Environmment} is the type of scopes or environments used for binding,
%%\emph{Null} is the type of the unique \c{NULL} object, \emph{Vector} is the type
%%assigned to vectors of strings, booleans, integers, reals and bytes;
%%\emph{Symbol} is the type of unevaluated symbols, and \emph{Function} is the
%%type of functions.
%%
%%
%%From the figure, we observe that majority of inputs to Core \eval functions are
%%expressions in contrast to package \eval calls which receive mostly environments
%%as inputs. In fact, \PackageEnvironmentEvalPerc of inputs to package evals are
%%environments.
%%
%%Now, we turn our attention to the expressions passed as input to \eval.

>>>>

We further investigate the type of input passed to \eval in
Figure~\cite{fig:eval-expression-kind} by the type of input and
the source of \eval. In this figure, \emph{Expression} is the type of program text,
\emph{Environmment} is the type of scopes or environments used for binding,
\emph{Null} is the type of the unique \c{NULL} object, \emph{Vector} is the type
assigned to vectors of strings, booleans, integers, reals and bytes;
\emph{Symbol} is the type of unevaluated symbols, and \emph{Function} is the
type of functions.

\begin{figure}[!h]
	\centering
  \includegraphics[width=\columnwidth]{eval-expression-kind}
  \caption{Type of Expression passed to \eval} \label{fig:eval-expression-kind}
\end{figure}

From the figure, we observe that majority of inputs to Core \eval functions are
expressions in contrast to package \eval calls which receive mostly environments
as inputs. In fact, \PackageEnvironmentInputEvalCallPerc of \eval calls in
packages receive environments as input expressions.

Now, we turn our attention to the expressions passed as input to \eval.
